\section{The final determination of merits of \mrls Extraordinary Ability}
\label{sec:Merits}

\mrls passion for software development started in middle school.
He was making free computer games as a hobby in his teen years.
As early as 2002, when he was 17, his games were downloaded hundreds of times per month from the internet
\ExhibitRef{Lehasoft}.

His games were even published on compilation CDs around 2003 at least twice
without him knowing \ExhibitRef{Cds}.

At the age of 18, \mrl started his first business around software.
He created a software marketplace GetSoft.ru for Russian audience in 2004 \ExhibitRef{GetSoft}.
At the peak, the website was visited by over 40 thousand unique visitors monthly \ExhibitRef{GetSoftStat}.

In 2005--2006, \mrl was working part-time in Telma, an international company
specializing in mobile software development.

From 2002 to 2006, \mrl was studying in \Nntu and graduated with honor as a Bachelor \ExhibitRef{Diploma1}.
From 2006 to 2008, he continued his education there and graduated with honor again
with an Engineer's degree, which is a Russian post-Bachelor education level.
All grades in his diploma were `excellent' \ExhibitRef{Diploma2}.

From 2006 to 2013, \mrl was making websites as a freelancer.

In 2011, he became an assistant to Sergey Gran and soon became a Chief Technology Officer
in his education center, which was a success as Mr. Gran puts it:

\ParagraphQuoteByExhibit{%
    Alexey's most important contribution to my company was that he was in charge of all IT-relatedwork we had.

    As a result of Alexey's work, we implemented efficient IT solutions in the areas of
    \ul{customer learning management, sales, payment procesing, email marketing, affiliate marketing, and others}.
    This allowed the company to accelerate its growth severalfold
    and helped \ul{increase the company's revenues fourfold} during the period from 2014 to 2015.

    At the peak, my company had \ul{over a hundred teachers, over 2500 students,
    and over a hundred active affiliate marketing partners} simultaneously.

    This scale became posible, among other things, thanks to efective IT solutions
    implemented by Alexey in various areas of the company's operations.%
}{\MrGranT}{LetterGran}

In 2019--2020, \mrl was working as a Senior PHP Developer at Calltouch,
a large advertising analytics platform in Russia.
He was performing critical duties there being in charge for the authentication system.

\ParagraphQuoteByExhibit{%
    During his employment, Alexey made a few significant contributions to our products:

    \ul{Critical vulnerability fixes}.
    We were making our authentication system more robust and flexible,
    and we needed the audit of the code that manages privileges.
    Alexey did that as part of his duties.
    \ul{He did find and fix critical vulnerabilities to the code before they were deployed and could be exploited.
    This can not be underestimated}.

    Authentication system refactoring.
    Apart from fixes, Alexey completed \ul{the migration to the more advanced system
    of managing privileges} and helped retire the old version.
    This freed a lot of resources busy with maintenance, and this itself \ul{improved
    the performance of the department}.%
}{\MrCalltouchT}{LetterCalltouch}

Also in 2020, \mrl made a large contribution to the industry.
He used his spare time to improve the most popular static analyzer tool for PHP programming language,
PHPStan.
It significantly improved analysis results cutting a lot of false-positive errors.
The importance of this is explained by <title> at Calltouch:

\ParagraphQuoteByExhibit{%
    To verify our software quality, our company used to rely on code reviews,
    tests, and the built-in hints of IDE (code editors).
    We did not use static analysis in our server-side workflows
    because the industry-standard tool PHPStan was showing
    a lot of false positive errors around variable types.
    In April and May 2020, Alexey used his spare time to improve that tool in a great way.
    This made it suitable for our workflows.
    He then helped us integrate the tool into our deployment process.
    This extra check \ul{significantly reduced accidental downtime
    and the frequency of required emergency fixes}.
    This improved the quality of our product and customer experience.
    This was critical because it was the time of the pandemic,
    and customers were jumping off easily in case of service disruptions.%
}{\MrCalltouchT}{LetterCalltouch}

This feature had an effect across the entire industry.
The popularity of PHPStan has grown dramatically since then,
with \ul{this code been downloaded over 130 million times after that} \ExhibitRef{PhpStanPackagist}

This is not surprising as PHP is the dominant language for website backend development,
over 76\% of the websites globally use PHP \ExhibitRef{PhpUsage}.

This is confirmed by Mr. \MrPhpOne, who is <title>:

\ParagraphQuoteByExhibit{%
    It's safe to say that this feature is widely used in the industry in companies of all sizes.%
}{\MrPhpOneT}{LetterPhpOne}

This is also confirmed by \MrPhpTwoT:

\ParagraphQuoteByExhibit{%
    This allowed PHPStan to be adopted in large projects without silencing type checks,
    which resulted in improved code quality and stability of projects in the industry.%
}{\MrPhpTwoT}{PhpTwoRecommendation}

In late 2020, \mrl began his interest in Flutter, a framework from Google for cross-platform
development of web, mobile, and computer applications.

In 2021, he took part in the largest Hackathon in Russia, `Digital Breakthrough'
as a member of `1DevFull' team in the role of System Architect \ExhibitRef{LodDefenseTeam}.
The team took the 3rd place in the case they were competing in \ExhibitRef{RsvNews}.

Also in 2021, \mrl started his technical blog on Medium.
As of writing, he has published 49 technical articles %UPDATABLE
and few non-technical ones
\ExhibitRef{MediumArticles}.

His articles were curated multiple times.
8 articles were chosen by Medium staff for recommendation beyond his followers \ExhibitRef{MediumStatsDistributed}.
One of his articles was chosen for a wide boost across Medium \ExhibitRef{SignInRoutesStats}.
Another article was posted in a specialized LinkedIn blog with over 95 thousand followers \ExhibitRef{FlutterDevsPost}.

In his blog on Medium, \mrl has over 600 followers. %UPDATABLE
It may seem not much, but that is the trait of this platform.
For comparison, the Google's product manager of Dart and Flutter
and the official announcer of Dart releases has just over 6 thousand followers there
\ExhibitRef{ThomsenFollowers}.
For a technical writer, having just 10 times less followers %UPDATABLE
than the maintainer of the language
he writes about should be considered a success after just two years of publishing.

In 2022--2023, \mrl was working for Akvelon, an international company headquartered in the United States.
For Akvelon, he performed the role of critical importance
leading its frontend contributions to Apache Beam:

\ParagraphQuoteByExhibit{%
    <\dots>%
}{\MrAkvelonT}{LetterAkvelon}

Apart from the work directly for Apache, \mrl has led the development
of a product that stayed the property of Akvelon:

\ParagraphQuoteByExhibit{%
    <\dots>%
}{\MrAkvelonT}{LetterAkvelon}

\MrEditorT witnesses:

\ParagraphQuoteByExhibit{%
    <\dots>

    Before those features,
    an editor in a Flutter app could only satisfy basic programmer's needs
    while leaving the feeling that it's still far from professional development tools available on computers.
    As a result, people would often write larger pieces of code in professional desktop editors
    and then copy and paste it into a Flutter app to use it there.

    The features developed by Mr. Inkin \ul{led to a paradigm shift
    where much more work can be done in a Flutter app directly,
    and professional desktop editors are less often needed.
    This is huge for the industry because it streamlines work,
    decreases dependency on desktop computers and makes more tasks achievable on just mobile devices}.

    This is already seen by the adoption of their editor.
    It became the second most popular one as measured by the package repository at pub.dev.
    It is already used in chats, online configuration editors, larger-scale online editors, and more.
}{\MrEditorT}{LetterEditor}

flutter\_code\_editor was the core component in two applications
that \mrl and the team he supervised developed for \Asf,
one of the largest open-source communities.
His role is confirmed by \MrApache:

\ParagraphQuoteByExhibit{%
    From 2022 to mid-2023,
    the Beam community developed two web applications
    to simplify learning Apache Beam by allowing users to write their code online
    and execute it on sandboxed backend servers without any installation\dots

    Mr. Alexey Inkin contributed to both of those applications from June 2022 to June 2023\dots
    His work included \ul{architecture design, authorship of 43 code changes,
    as well as a leading role, reviewing 47 code changes from three other frontend developers}.

    Mr. Inkin's contribution was central to the completion of those projects on time
    for the annual Beam Summit conference of 2023,
    which is the main event for the project where we make announcements and showcases,
    and it was attended by 592 people including online participants.
    The two applications have now been used by over 3000 people.%
}{\MrApacheT}{LetterApache}

Independently of Akvelon, \mrl authored and maintains 23 open-source software packages for Flutter
including popular ones \ExhibitRef{PubAinkin}.

He contributed code to a few Flutter packages with the popularity of 96\%
and one package owned by Google with the popularity of 99\%
(more popular than 99\% of all packages in Dart) \ExhibitRef{FlutterContributions}.

All of his open-source contributions were important enough that combined with his expert knowledge
they earned the title of `Google Developer Expert' for him \ExhibitRef{GdeBadgeAwarded},
and this is how Google officially characterizes him:

\ParagraphQuoteByExhibit{%
    He is part of the Google Developer Experts (GDE) community.
    The GDE program is a global network of highly experienced technology experts,
    influencers, and thought leaders who have expertise in Google technologies,
    are active leaders in the space, natural mentors,
    and contribute to the wider developer and startup ecosystem.
    Nearly a thousand Experts represent Google technologies around the world,
    whereas there are about 105 Dart \& Flutter technologyexperts.
    Alexey Inkin has been one of them since Jul 27, 2023.%
}{\MrGoogleT}{LetterGoogle}

Although the award is recent, it required a long record of contributions.
The application guide of the GDE program names two years as a guideline:

\ParagraphQuoteByExhibit{%
    Make sure to fill out the form carefully and to showcase your impact and contributions
    for a prolonged period of time (\ul{ideally, at least 2 years}).
    Successful GDE candidates have a long track record of tech talks or written content they created themselves.%
}{GDE application guide, `Application Process' page}{GdeApplicationGuide}

This indicates that \mrl had sustained acclaim for at least two years by the summer of 2023.

Even longer record of significant performance is required for the Senior membership of the \Ieee,
which \mrl was awarded in September 2023 \ExhibitRef{IeeeElevationNotification}.
From the requirements,

\ParagraphQuoteByExhibit{%
    Candidates shall have been in professional practice for at least ten years.

    Candidates shall have shown \ul{sianificant performance over a period of at least five of those years}.%
}{IEEE Senior member requirements page}{IeeeSeniorRequirements}

This is the world's largest technical professional organization \ExhibitRef{Samsung}.

Furthermore, \mrl was trusted to judge the new applicants for the IEEE Senior membership
\ExhibitRef{IeeeJudgingThankYou}.

\mrl was also approved by \Siia (SIIA) to judge their 2024 CODiE award \ExhibitRef{CodieApproved}.
This organization and the award have long history.
The organization was established in 1984 as `\Spa'.
It had been hosting the `Excellence in Software Award' since 1986 \ExhibitRef{SiiaWikipedia}.
The award was labeled `Oscars in Software' by Los Angeles Times \ExhibitRef{CodieLatimes}
and Washington Post \ExhibitRef{CodieWp}.
The association was renamed to \Siia after merging with \Iia in 1999 \ExhibitRef{SiiaWikipedia},
when the two were named \QuoteByExhibit{two of the most powerful computer-related trade groups}{Wired}{SiiaWired},
and the award was renamed to CODiE \ExhibitRef{CodieRename}.

This track record clearly shows the extraordinary ability of \mrl.

From those recent achievements and Google's naming him an expert
and putting him to \ul{top 0.025\%} of experts in his technology,
it is evident that he has risen to the very top of the field of Software Development,
as required by 8 C.F.R. §204.5(h)(2).

From at least 2 years of required achievements for the Google Developer Experts program,
5 years of significant performance mandated by IEEE,
and from the approval as a judge for the `Oscars in Software',
it is evident that he has sustained national or international acclaim
and that his achievements have been recognized in the field of his expertise
as required by 8 C.F.R. §204.5(h)(3).

\pagebreak


%Lehasoft TankBattle:
%628 monthly
%https://web.archive.org/web/20030104004237/http://online.download.ru:80/program.ehtml?ProgramID=11268
%
%Lehasoft Dyna
%176 monthly
%https://web.archive.org/web/20030925125216/http://online.download.ru/program.ehtml?ProgramID=11592
%
%Lehasoft Dyna DM
%248 all-time by 2007
%https://web.archive.org/web/20070324093153/http://www.download.ru/soft/arcade/games__entertainment/Lehasoft_Dyna_DM/11592
%
%Lehasoft Tetris
%347 monthly
%https://web.archive.org/web/20021019072912/http://online.download.ru/program.ehtml?ProgramID=10100
%
%
%
%Русская игротека 2003
%https://gamestracker.org/torrents/pc/action/russkaja_igroteka_2003_400_igr_na_russkom_dlja_windows/15-1-0-37113
%
%
%Сборник игр для мальчиков
%http://www.torrentsbornik.ru/torrent/igry/161998_sbornik_igr_dlya_malchikov_piratka
