\subsubsection{Calltouch}
\label{subsubsec:RoleCalltouch}

\SubSubSubSection{Context}

Calltouch is a marketing internet service in Russia.

The distinguished reputation of the company and \mrls role in it
will be shown below.

\SubSubSubSection{Proof of \mrls past employment at Calltouch}

\mrl was employed in Calltouch since July 29, 2019, until September 18, 2020.
The employment and the start date are proven by his contract with Calltouch \ExhibitRef{CalltouchContract}.


\SubSubSubSection{Proof of \mrls performing a critical role at Calltouch}

Here is the quote from a letter by \MrCalltouchT:

\ParagraphQuoteByExhibit{%
    During his employment, Alexey made a few \ul{significant contributions} to our products:

    \textbf{Critical vulnerability fixes}.
    We were making our authentication system more robust and flexible,
    and we needed the audit of the code that manages privileges.
    Alexey did that as part of his duties.
    \ul{He did find and fix critical vulnerabilities to the code before they were deployed
    and could be exploited.
    This can not be underestimated}.

    \textbf{Authentication system refactoring}.
    Apart from fixes, Alexey completed the migration to the more advanced system
    of managing privileges and helped retire the old version.
    This \ul{freed a lot of resources busy with maintenance},
    and this itself improved the performance of the department.

    \textbf{A tool to visualize the privilege tree}.
    A side effect of authentication system migration was duplication of privileges
    and redundancy in role inheritance.
    We only had textual representation of the role tree in our database.
    Alexey had developed a tool to build that tree visually
    to easily detect redundancy so it can be removed.
    This \ul{reduced mental resources required to maintain the system}.

    \textbf{PHPStan improvement}.
    To verify our software quality, our company used to rely on code reviews, tests,
    and the built-in hints of IDE (code editors).
    We did not use static analysis in our server-side workflows
    because the industry-standard tool PHPStan was showing
    a lot of false positive errors around variable types.
    In April and May 2020, \ul{Alexey used his spare time to improve that tool in a great way.
    This made it suitable for our workflows.
    He then helped us integrate the tool into our deployment process.
    This extra check significantly reduced accidental downtime
    and the frequency of required emergency fixes.
    This improved the quality of our product and customer experience.
    This was critical because it was the time of the pandemic,
    and customers were jumping off easily in case of service disruptions}.%
}{\MrCalltouchT}{LetterCalltouch}

<Title> defines \mrls role in the company as critical
providing multiple proofs.

According to the USCIS policy,

\ParagraphQuoteByExhibit{%
    Examples of lead or critical roles may include, but are not limited to:
    \dots
    critical role for a distinguished organization or a distinguished division
    of an institution or company, as explained in detail by the director
    or a principal investigator of the relevant organization or division.%
}{\PolicyManual}{RoleUscisPolicy}

This makes \mrls role in Calltouch critical for the purpose of this petition.


\SubSubSubSection{Proof that Mr. \MrCalltouch is <Title>}

<Page> shows that \MrCalltouch is <Title>
\ExhibitRef{CalltouchRole}.

Additionally, this position is shown on Mr. \MrCalltouch's LinkedIn Page \ExhibitRef{CalltouchLinkedIn}.


\SubSubSubSection{Proof that Calltouch is a distinguished organization}

The revenue of Calltouch for 2019 was announced in `Vedomosti' newspaper:

\ParagraphQuoteByExhibit{%
    Calltouch's revenue for 2019 was approximately 700 million rubles.%
}{`Vedomosti' newspaper}{CalltouchSoldVedomosti}

The Central Bank of Russia shows that
61.9057 Russian Rubles was the equivalent of 1 United States dollar on the last day of 2019
\ExhibitRef{CalltouchCbr}.

This makes the revenue of Calltouch in 2019 being around

\[
    \frac{700\:million\:RUB}{61.9057\:\frac{RUB}{USD}} \approx 11.3\:million\:USD
\]

That piece of news also reads that

\ParagraphQuoteByExhibit{%
    \dots it is the largest M\&A deal involving a marketing analytics service in the Russian market.%
}{`Vedomosti' newspaper}{CalltouchSoldVedomosti}

`Vedomosti' newspaper is a reputable source for such data as indicated by its Wikipedia page:

\ParagraphQuoteByExhibit{%
    Vedomosti was founded in 1999 as a joint venture between Dow Jones,
    who publishes \ul{The Wall Street Journal}; Pearson, who previously published the \ul{Financial Times};
    and Independent Media, who publishes The Moscow Times.%
}{Wikipedia page for Vedomosti}{VedomostiWikipedia}

That high revenue cited by that reputable source makes Calltouch a distinguished organization
for the purpose of this petition.
