\section{Summary of \mrls achievements and qualifications}

\mrl is an engineer specializing in software development, see his resume in \ExhibitRef{Resume}.
He graduated from \Nntu with honors.
He has a Bachelor's degree \ExhibitRef{Diploma1}
and an Engineer's degree (a post-Bachelor degree in Russia) in Information Technology \ExhibitRef{Diploma2}.

In his 19 years in the profession, he was working in the areas of backend software development with PHP
and frontend software development with Flutter, a technology from Google.

\mrl was awarded a title of `Google Developer Expert',
a prestigious award from Google \SectionRef{subsubsec:AwardGde}.
He also held a podium place in `Digital Breakthrough',
a large nationally recognized hackathon in Russia \SectionRef{subsubsec:AwardLod}.

\mrl is a Senior Member of \Ieee, the largest professional association for engineers.
The prestigious Senior Membership requires extensive significant performance \SectionRef{subsubsec:AssociationsIeee}.
\mrl is also a member of `Google Developer Experts' community.
This membership requires outstanding achievements
with about thousand members in total and just over 100 members specializing in Flutter.
This puts him in top 0.025\% of the developers who actively use Flutter \SectionRef{subsubsec:AssociationsGde}.

\mrl was invited to judge new applicants to Senior Membership of IEEE
and received a Thank You letter from the chair of the committee
that reviews the applications and promotes members \SectionRef{subsec:Judging}.

\mrl performed critical role in multiple distinguished organizations.
He was a developer and a leader of the team that developed frontend
for two important applications for \Asf, one of the largest open-source foundations
\SectionRef{subsubsec:RoleApache}.
This was done during his employment at Akvelon, an international company headquartered in the United States.
For Akvelon, he lead the development of a specialized code editor in Flutter,
which not only became the central part of those Apache applications but also a valuable product of its own
\SectionRef{subsubsec:RoleAkvelon}.
Before that, \mrl worked for Calltouch, a large Russian platform for advertising analytics.
He was in charge of the authentication system there, finding and fixing
security issues, which is critical by definition \SectionRef{subsubsec:RoleCalltouch}.
He also was a CTO for Mr. Sergey Gran, the founder of \GSchool,
implementing technical solutions that increased the company's revenue severalfold \SectionRef{subsubsec:RoleGran}.

\mrl made contributions of major importance to the field of \fie.
He designed and implemented a major feature in PHPStan, the most popular static analyzer
of code in PHP programming language.
This feature reduced false-positive errors reported by the analyzer
and reduced the burden to correctly document the code for the analyzer to work properly.
This had major effect since PHP powers the majority of websites worldwide \SectionRef{subsubsec:ContributionsPhpStan}.
Also, the code editor for Flutter that the team of \mrl developed
became the second most popular editor for that framework and is used in many applications
\SectionRef{subsubsec:ContributionsFlutter}.

\mrl commanded higher salary during his employment at Akvelon,
3 times higher than the average in Information Technology in the country of Georgia,
and 2.02 times higher than the average in Software Development \SectionRef{subsec:Salary}.

\mrl has authored 49 technical articles in his blog on Medium.
9 of them were curated for wider online publication \SectionRef{subsec:Articles}.

\pagebreak
