\subsubsection{Akvelon}
\label{subsubsec:RoleAkvelon}

\SubSubSubSection{Context}

Akvelon is a United States company with multiple overseas offices.
\mrl was employed in Akvelon's office in the country of Georgia.

It was Akvelon who was officially working with \Asf on the two applications
discussed earlier, which is proven by the announcement in the Apache Beam blog:

\ParagraphQuoteByExhibit{%
    Please give a huge thank you to our Akvelon, Inc. team
    for releasing our new Apache Beam Playground!%
}{Apache Beam blog post}{BeamAkvelonAnnouncement}

It was Akvelon who hired \mrl to work on the applications (`Beam Playground' and `Tour of Beam')
for \Asf discussed earlier.
Thus that work of \mrl counts towards his roles in both Apache and Akvelon.

\SubSubSubSection{Proof of \mrls past employment at Akvelon}

\mrl was employed in Akvelon as a Software Development Engineer since June 6, 2022, until June 16, 2023.
The employment, the position, and the start date are proven by his contract with Akvelon \ExhibitRef{AkvelonContract}.


\SubSubSubSection{Proof of \mrls performing a critical role in Akvelon}

Here is the quote from a letter by \MrAkvelonT:

\ParagraphByExhibit{%
    ``\dots"
}{\MrAkvelonT}{LetterAkvelon}

The <Title> witnesses that the work of \mrl was both leading and critical.

According to the USCIS policy,

\ParagraphQuoteByExhibit{%
    Examples of lead or critical roles may include, but are not limited to:
    \dots
    critical role for a distinguished organization or a distinguished division
    of an institution or company, as explained in detail by the director
    or a principal investigator of the relevant organization or division.%
}{\PolicyManual}{RoleUscisPolicy}

This makes \mrls role in Akvelon critical for the purpose of this petition.

That leading position of \mrl is additionally confirmed in the announcement of Flutter Code Editor
on Akvelon's website. \mrl is listed there as the first of the team members
and as a \Quote{Lead Flutter Developer at Akvelon} \ExhibitRef{AkvelonFceAnnouncement}.

\mrls position of \Quote{Lead Flutter Developer} is reiterated in two other corporate blog posts
\ExhibitRef{AkvelonBlog}


\SubSubSubSection{Proof that Mr. \MrAkvelon is a <Title>}

Mr. \MrAkvelon is <Title> as he had been <\dots>

Additionally, he is a <Title>, which is shown:

\begin{itemize}

    \item On his LinkedIn page \ExhibitRef{AkvelonLinkedIn}

    \item On <\dots> \ExhibitRef{AkvelonRole}

\end{itemize}


\SubSubSubSection{Proof that Akvelon is a distinguished organization}

Akvelon is over 23 years old, has over 1200 employees, over 150 customers, and has 15 offices globally.
Its customers include Google and Microsoft \ExhibitRef{AkvelonAbout}.

As an independent indicator, USCIS routinely approves working visas for Akvelon,
including many H-1B petitions \ExhibitRef{AkvelonUscis}.

This makes Akvelon a distinguished organization for the purpose of this petition.
