\section{%
    \mrls proposed employment has both substantial merit and national importance for the United States%
}
\label{sec:Benefit}

\Bea has reported that in 2021 the Digital Economy contributed
10.3\% of the United States GDP or \$2.4 trillion.
On average since 2016, this amount has been growing
by 6.7\% annually, adjusted for inflation, which is above the overall economy.
The digital economy comprises 8 million jobs in the United States,
with 2\% average annual growth \ExhibitRef{BeaDigitalEconomyBig}.

Moreover, this has recently accelerated:

\ParagraphQuoteByExhibit{%
    Growth in price-adjusted GDP (also referred to as `chained-dollar' or `real'
    GDP) was \ul{9.8 percent} in 2021, \ul{greatly outpacing growth in the overall economy},
    which increased 5.9 percent.%
}{\Bea report on Digital Economy for 2021}{BeaDigitalEconomy}

\mrls field of interest is \fie, which is central to the Digital Economy.
Out of \$3.7 trillion gross output, it is responsible for \$722 billion
and has shown even stronger growth of 12.1\% in 2021 \ExhibitRef{BeaDigitalEconomy}.

Of that \$722 billion, over \$170 billion is mobile software according to Statista \ExhibitRef{StatistaMobileUs}.
On that mobile software market, Flutter is the leading cross-platform development framework \ExhibitRef{FlutterStatista},
which cuts engineering effort by 70\% compared to separate development for Android and iOS \ExhibitRef{FlutterGooglePay}.

In that Flutter technology, \mrl is recognized as an expert by Google, the creator of the technology:

\ParagraphQuoteByExhibit{%
    There are about 105 Dart \& Flutter technology experts.
    Alexey Inkin has been one of them since Jul 27,2023.%
}{\MrGoogleT}{LetterGoogle}

Since \QuoteExhibit{nearly half a million developers now using Flutter each month}{Flutter2M},
\mrl is in about \ul{top 0.025\%} of all developers who use it.

If \mrl worked in the United States, it would be easier for him to share his knowledge and expertise
to the wide community of other engineers further improving the quality, cutting costs and improving
pace of software development in the United States.

Nationwide, transition of more mobile applications to Flutter has the potential of saving tremendous amount
of engineering effort and reducing cost, which will help the United States vendors in global competition.

As the president of the United States said,

\ParagraphQuoteByExhibit{%
    We are in competition with China and other countries to win the 21st century\dots
    We are at a great inflection point in history.
    We have to do more than just build back better\dots We have to compete more strenuously\dots
    We have to develop and dominate the products and technologies of the future.%
}{\MrBidenT}{CnbcBidenCompetition}

In that international conditions,
on the market that large and that centric as Software Development,
\mrls permanent residency is of national importance,
and it will bring substantial benefit to the United States.

\pagebreak
