\subsubsection{Google Developer Experts (GDE) Membership}
\label{subsubsec:AssociationsGde}

The \mrls title of `Google Developer Expert'
was already mentioned in an earlier criterion \SectionRef{subsubsec:AwardGde}.
However, beside the award this is also a prestigious membership.

\SubSubSubSection{Proof of \mrl being a member of Google Developer Experts}

The GDE membership of \mrl is confirmed by his public profile on Google's website.
Among other badges, he has the one that reads
\QuoteExhibit{Google Developer Experts member}{GdeBadgeAwarded}

Another proof of his current membership is the letter from Google:

\ParagraphQuoteByExhibit{%
    <\dots>
    He is part of the Google Developer Experts (GDE) community\dots
    Alexey Inkin has been one of them since Jul 27, 2023.%
}{\MrGoogleT}{LetterGoogle}


\SubSubSubSection{Proof of GDE being a community in \mrls field of \fie}

The same supporting letter from Google highlights the focus of the community:

\ParagraphQuoteByExhibit{%
    The GDE program is a global network of highly experienced \ul{technology experts},
    influencers, and thought leaders who have \ul{expertise in Google technologies},
    are active leaders in the space, natural mentors,
    and \ul{contribute to the wider developer and startup ecosystem}.%
}{\MrGoogleT}{LetterGoogle}

Finally, the word \Quote{Developer} in `Google Developer Experts' shows that the community
is in \mrls field of \fie.


\SubSubSubSection{Proof that outstanding achievements are required for GDE membership}

On the home page of the community, the eligibility criteria include the following:

\ParagraphByExhibit{%
    ``Eligibility criteria:

    \begin{itemize}

        \item \ul{Solid expertise in an area featuring Google technology} such as Android,
        Google Cloud, Machine Learning, Web and more.
        You do not need a formal education to be considered for the GDE program.

        \item Display \ul{significant contributions} in the developer community
        including but not limited to speaking at events, publishing content,
        mentoring other developers and companies."

    \end{itemize}
}{\GdeHome}{GdeHome}

The word \Quote{outstanding} is not used specifically, but that level of requirements
is evident from the small number of experts in the community.

The home page of the community reads:

\ParagraphQuoteByExhibit{%
    A global network of more than 1,000 professionals.%
}{\GdeHome}{GdeHome}

And the supporting letter from Google reads:

\ParagraphQuoteByExhibit{%
    \ul{Nearly a thousand Experts} represent Google technologies \ul{around the world},
    whereas \ul{there are about 105 Dart \& Flutter technology experts}.
    Alexey Inkin has been one of them since Jul 27, 2023.
}{\MrGoogleT}{LetterGoogle}

This proves that the word \Quote{outstanding} may be applied to achievements
required for this membership.

For context, Dart is the programming language which is used in Flutter technology,
they come together often in this petition.


\SubSubSubSection{%
    Proof that GDE applicants are judged by recognized
    national or international experts in their fields
}

The \GdeApplicationGuide details on the application process and the review stages.
It shows the following stages:

\ParagraphQuoteByExhibit{%
    The application process for the Experts program consists of 3 steps:
    application form, the community interview and the product interview.

    \dots

    Once you are past the application form step, you will be matched with
    \ul{one of the current Google Developer Experts} for the Community Interview.
    The aim of this interview is to get to know you, your motivation to join the
    program and your expertise in the category you are applying for.%
}{\GdeApplicationGuide}{GdeApplicationGuide}

This proves that existing internationally recognized experts judge the applicants,
as the EB-1A program requires.

At this stage, \mrl was evaluated by \MrGdeMemberInterviewer,
as shown in the invitation for the interview \ExhibitRef{GdeMemberInterviewerInvitation}.
He is a Google Developer Expert
and a Senior developer at <\dots>.
His experience is shown on his LinkedIn page \ExhibitRef{GdeMemberInterviewerLinkedIn}.

Finally, after that stage there is an even more elaborate knowledge and experience evaluation:

\ParagraphQuoteByExhibit{%
    After passing the Community Interview, this
    time you will be \ul{matched with a Googler} for a Product Interview.
    The interviewer will focus mostly on your technical knowledge and
    expertise.%
}{\GdeApplicationGuide}{GdeApplicationGuide}

\Quote{Googler} is an informal term for a Google employee.

At this stage, \mrl was evaluated by \MrGdeGoogleInterviewer,
as shown in the invitation for the interview \ExhibitRef{GdeGoogleInterviewerInvitation}.
He is an engineer at Google.
His experience is shown on his LinkedIn page \ExhibitRef{GdeGoogleInterviewerLinkedIn}.
He is a public figure and has over <many> followers on Twitter \ExhibitRef{GdeGoogleInterviewerTwitter}.

Google developers are sure recognized experts in the technology they create,
which also counts towards the requirement of being judged by internationally recognized experts.
