\UnnumberedTitle{%
    Statement from \mrl detailing plans on how he intends to continue work in the United States%
}
\label{WorkPlan}

My name is \fl.
I am the beneficiary of this I-140 Immigrant Petition for Alien Worker,
seeking EB-1A classification as an individual of extraordinary ability.
I have a vast experience in the field of \fie,
and I intend to continue my employment in this field in the United States.

I am going to continue my focus on developing using Flutter,
which is the world's most popular technology for cross-platform
web and mobile applications \ExhibitRef{FlutterStatista}.

This is in high demand, as the global revenue from mobile apps worldwide
has been steadily growing in the recent years and is projected to grow
regardless of the ongoing problems in other markets.
The growth in 2024 over 2023 is expected to be 11\% (\$603B from \$542B) \ExhibitRef{AppsRevenue}.

I plan to reside in the state of Texas.
LinkedIn alone shows almost 100 job posts for Flutter in Texas \ExhibitRef{LinkedInFlutterJobs},
and my resume matches most of them even before accounting for my awards.

My membership and title of `Google Developer Expert in Flutter'
make me one of the top applicants for any Flutter position.
Moreover, to maintain this membership, which contributes a lot to my prominence,
I must continue my work in this field, so I have a strong incentive to do so.

I will also leverage my Senior membership in the \Ieee,
which is headquartered in New York City with a lot of their events happening in the United States.
This membership has a lot of networking opportunities
with high potential for getting consulting contracts.

A permanent residency in the United States will increase my experience, networking,
and learning opportunities even more, since the United States is the world's center
of technology advancement.
Some of my communication with Google and its employees will become in-person instead of being online,
which improves the experience.

In parallel to a full-time job, I will continue my service as private consultant.
I get traffic for this from my prominence on Google's website \ExhibitRef{GdeBadgeAwarded}.
Showing a United States location there will further boost the traffic
as many of the United States customers prefer domestic consultants.

Sincerely,

\fl

\begin{tabular}{ll}
    Email: & <\dots>\\
    Phone: & <\dots>\\
    Address: & <\dots>, Batumi, 6000, Georgia\\
\end{tabular}

\pagebreak
