\subsubsection{Google Developer Expert Award}
\label{subsubsec:AwardGde}

\SubSubSubSection{Proof of \mrl being the recipient of the award}

\mrl was awarded the title of Google Developer Expert in 2023.
This can be verified at his public profile on Google's website.
A badge in the profile reads:

\ParagraphQuoteExhibit{%
    Was awarded the title of Google Developer Expert in 2023.%
}{GdeBadgeAwarded}

This award is granted together with the membership in the Google Developer Experts program,
as explained in the description of the award badge:
\QuoteExhibit{Earn this badge by becoming a Google Developer Expert.}{GdeBadgeDetails}.
The supporting letter to \mrl from Google confirms his current membership
and thus additionally confirms the award:

\ParagraphQuoteByExhibit{%
    He is part of the Google Developer Experts (GDE) community\dots
    Alexey Inkin has been one of them since Jul 27, 2023.%
}{\MrGoogleT}{LetterGoogle}


\SubSubSubSection{Proof of the criteria being excellence in the field}

The home page of the Google Developer Experts program shows these among the eligibility criteria:

\ParagraphByExhibit{%
    \begin{itemize}%
%
        \item ``\ul{Solid expertise} in an area featuring Google technology such as Android,
        Google Cloud, Machine Learning, Web and more.
        You do not need a formal education to be considered for the GDE program.

        \item Display \ul{significant contributions in the developer community} including
        but not limited to speaking at events, publishing content,
        mentoring other developers and companies."

    \end{itemize}
}{\GdeHome}{GdeHome}

This proves that the basis for granting the award is excellence in the field.


\SubSubSubSection{Proof of no limitation to competitors except begin 18+ years old}

On the same home page, the complete eligibility criteria read like this:

\ParagraphByExhibit{%
    ``Google Developer Experts have \ul{a variety of diverse backgrounds}.
    They are developers, founders, mothers, activists, and so much more.
    The one thing they have in common is that they're passionate professionals
    with expertise in Google technology who enjoy continuous learning,
    sharing knowledge, and making an impact on the community.

    Eligibility criteria:

    \begin{itemize}

        \item Solid expertise in an area featuring Google technology such as Android,
        Google Cloud, Machine Learning, Web and more.
        \ul{You do not need a formal education to be considered for the GDE program}.

        \item Display significant contributions in the developer community
        including but not limited to speaking at events, publishing content,
        mentoring other developers and companies.

        \item Ability to articulate clearly and provide meaningful advice to others.

        \item \ul{Must be 18+ years old}.

        \item Ability to interview and communicate in English as it's the official language
        of the program."

    \end{itemize}
}{Google Developer Experts home page}{GdeHome}

It mentions diverse background, no need for any formal education,
and the only limiting factor is the minimal age of 18 years old.

This further increases the significance of the award, because almost all developers can compete for it.

\SubSubSubSection{Proof of the international recognition of the award}

The same supporting letter from Google highlights the significance,
the international status, and the rareness of the award:

\ParagraphQuoteByExhibit{%
    The GDE program is a global network of \ul{highly experienced technology experts,
    influencers, and thought leaders who have expertise in Google technologies,
    are active leaders in the space}, natural mentors,
    and contribute to the wider developer and startup ecosystem.
    Nearly a thousand Experts represent Google technologies \ul{around the world},
    whereas \ul{there are about 105 Dart \& Flutter technology experts}.
    Alexey Inkin has been one of them since Jul 27, 2023.%
}{\MrGoogleT}{LetterGoogle}

For context, Flutter is a technology developed by Google for cross-platform development of web, mobile, and computer apps.

The significance of the award is additionally emphasized by the benefits that a recipient gets:

\ParagraphByExhibit{%
    ``Google supports Experts in many ways. Some of them may include:

    \begin{itemize}

        \item recognizing their skills via Experts website and badges that
        Experts may use in their social media profiles or personal websites,

        \item facilitating access to Google product teams and projects,
        including early access programs,

        \item invitations to Google events around the world,

        \item \ul{supporting travel} to conferences where they can speak about their
        favorite technologies."

    \end{itemize}
}{\GdeApplicationGuide}{GdeApplicationGuide}

Next, Google Developer Expert status is recognized beyond Google by industry leading companies.
For instance, JetBrains, the world's second most popular vendor of professional
code editors for programmers provides a lot of benefits for Google Developer Experts
\ExhibitRef{GdeJetBrains}.

Next, the LinkedIn page of Google Developer Experts community is followed by
three times more people than the page of Academy of Motion Picture Arts and Sciences
(those who administrate Oscars), which indicates the high professional interest
in the program and the award \ExhibitRef{GdeOscarsFollowers}.

Lastly, there are very few Google Developer Experts in Flutter, only about 105 worldwide
\ExhibitRef{LetterGoogle}, while Flutter is a popular technology:

\ParagraphQuoteByExhibit{%
    We continue to see fast growth in Flutter usage,
    with \ul{over two million developers having used Flutter} in the sixteen months since we released.
    Despite these unprecedented circumstances,
    in March we saw 10\% month-over-month growth,
    with \ul{nearly half a million developers now using Flutter} each month.%
}{\MrSneathT}{Flutter2M}

This award puts \mrl:

\begin{itemize}
    \item to about top 0.025\% of the developers who use Flutter technology each month.
    \item to top 0.00525\% of those attempted this technology.
\end{itemize}

