\Exhibit{Resume}{Resume of \mrl}

\UnnumberedTitle{Alexey Inkin}

\begin{tabular}{ll}
    Email: & <\dots>\\
    Phone: & <\dots>\\
    Telegram: & <\dots>\\
    Address: & <\dots>, Batumi, 6000, Georgia\\
    LinkedIn: & https://www.linkedin.com/in/alexey-inkin-784b7371/\\
    GitHub: & https://github.com/alexeyinkin\\
    Medium: & https://medium.com/@alexey.inkin\\
    Instagram: & https://www.instagram.com/alexey.inkin/\\
    VK: & https://vk.com/ainkin\\
\end{tabular}

\UnnumberedTitle{Skills}

\begin{itemize}
    \item Programming: Dart, Flutter, PHP, JavaScript, TypeScript, C++, Java, SQL.
    \item Technology: Git, GitHub Workflows, RabbitMQ, Google Cloud, Gradle, HTML, CSS.
    \item Management: Software project management, Team leadership.
    \item Languages: English (fluent), Russian (native).
\end{itemize}

\UnnumberedTitle{Membership}

\begin{tabular}{rl}
    July 2023 -- & Google Developer Experts, Dart \& Flutter Expert\\
    July 2023 -- & \Ieee (Senior Member since September 2023)
\end{tabular}

\UnnumberedTitle{Work Experience}

\ResumeItem{Lead Flutter Developer}{Akvelon}{June 2022 -- June 2023, Tbilisi, Georgia, Remote}{%
Leading front-end teams for Google and Apache projects.
Fully designed and led the implementation of:

— Apache Beam Playground frontend, https://play.beam.apache.org\\
— Tour of Beam frontend, https://tour.beam.apache.org\\
— Flutter Code Editor with code folding and more, https://pub.dev/packages/flutter\_code\_editor\\
— Porting HighlightJS to Dart, https://pub.dev/packages/highlighting

Responsibilities:

— Planning milestones.\\
— Designing architecture.\\
— Developing rich code editors and LMS.\\
— Defending solutions before Google engineers who develop Apache Beam.\\
— Reviewing code.\\
— Interviewing job candidates.\\
— Mentoring developers.\\
— Presenting the apps at a conference.
}

\ResumeItem{Flutter Team Leader}{Boss of Life}{May 2021 -- February 2022, London, United Kingdom, Remote}{%
— Mentoring junior developers.\\
— Implemented $\sim$40 mobile app screens.\\
— Designed the Firebase DB structure.\\
— Implemented the backend with $\sim$100 Firebase Cloud Functions.\\
— Security audit.\\
— Managed the acceptance testing.
}

\ResumeItem{Senior PHP Developer}{Calltouch}{July 2019 -- September 2020, Moscow, Russia, On-site}{%
— Auth system refactoring, finding and fixing security breaches.\\
— Ad report generation with lots of metrics and statistics from various external platforms, mapping large amounts of data.\\
— Notifications via Telegram Messenger.\\
— Configuring static code analysis with PHPStan.\\
— Improving test coverage with Codeception.

Tech includes PHP 7.1, Symfony 3, PostgreSQL 9.6, RabbitMQ, Redis, Docker, GitLab, Jira, Confluence, Crucible.

Calltouch is the leading call tracking provider in Russia with high load servers.
}

\ResumeItem{Senior PHP Developer}{Self-Employed}{January 2017 -- July 2019, Russia}{%
My own learning management system and e-commerce engine.
Tech includes:

— PHP 7.3, JavaScript, HTML5, CSS3, jQuery, MySQL.\\
— Continuous integration using Git, PHPStan, PHPUnit.\\
— Java Swing and ffmpeg to preprocess and upload video lessons.\\
— Facebook API and VK API for auth.\\
— Google Maps API to spot and view customers on a map.\\
— UniSender for email marketing.

The system comprises:

— Video lessons chaining, various access levels for students, automated and manual access granting.\\
— Video download protection against all browser plug-ins using HLS encryption and disposable links to
video segments.\\
— Online store that integrates major Russian payment service providers (Yandex, Tinkoff).\\
— Affiliate marketing engine with each traffic provider having their own Google Analytics account.
}

\ResumeItem{Chief Technology Officer}{Sergey Gran's Training Center}{November 2014 -- April 2016, Saint Petersburg \& Kazan, Russia, On-site}{%
As a CTO, I have:

— Developed an online Learning Management System.\\
— Integrated a 3rd party affiliate marketing engine.\\
— Designed an automated funnel that hired 100+ remote part-time teachers.

As a chief editor, I have:

— Hired graphic designers, illustrators, video editors, text transcribers and editors.\\
— Got a 100 hours of raw camera video and handwritten sketches to fully designed and published slideshows with animation effects.\\
— Wrote 150 pages of exercises for students. These included startup business strategies, life management, ad planning etc.\\
— Designed ads for high click-through ratio.

Revenue peaked at \$750'000 in 2015 out of which \$350'000 was the owner's profit.
That is 50 times the average income in Russia.

Sergey Gran's Training Center was selling video courses on business.
They had 2500 customers with
products ranging from \$100 to \$1500.

Tech included PHP 5, MySQL, CSS3, jQuery.
}

\ResumeItem{Founder}{GetSoft.ru}{December 2003 -- March 2014}{%
GetSoft.ru website brought together 3000 small software businesses and customers before Windows
Market was conceived.
The whole thing was free to everyone, and I had been selling ads for living.
Tech included PHP 4, JavaScript, CSS2, MySQL.
}

%\ResumeItem{PHP Developer}{}{2009--2013, Nizhny Novgorod, Russia}{%
%Short projects for gyms, dentists, fire safety, factories, and dozens of other small businesses.
%}

\ResumeItem{.NET Developer}{Telma}{February 2005 -- March 2006, On-site, Part-time}{%
Improving a proprietary system for contract management and an internal communication platform.
}

\UnnumberedTitle{Awards}

\begin{tabular}{r|l}
    2023 & Google Developer Expert\\
    2021 & `Medicine, Healthcare, and Science' National Hackathon,\\
    & `Leaders of Digital' Hackathon Series, Russia, 3rd place in iHerb's case\\
\end{tabular}

\UnnumberedTitle{Education}

\ResumeItem{Engineer, Information Systems and Technologies}{Nizhny Novgorod State Technical University}{September 2002 -- January 2008, Nizhny Novgorod, Russia}{%
The Engineer degree is a post-Bachelor education level in Russia.
}

\UnnumberedTitle{Volunteering}

\ResumeItem{Senior Member Review Panel Member}{\Ieee}{Since November 2023}{}

\ResumeItem{Presidential Election Observer}{NGO `Golos', Mikhail Prokhorov's HQ, Grigory Yavlinsky's HQ}{2012, 2018, Nizhny Novgorod, Russia}{}

\pagebreak
