\subsubsection{`Digital Breakthrough' hackathon, 3rd place, team competition}
\label{subsubsec:AwardLod}

\SubSubSubSection{Context}

\mrl was part of `1DevFull' team, which placed 3rd in `Digital Breakthrough' hackathon
on June 20, 2021.
The team was competing to solve the case of `iHerb', a United States online retailer,
which partnered with the competition organizer.
There were six cases (categories) in total \ExhibitRef{RsvNews}.

The key role of \mrl in the team and the significance of the award will be shown below.


\SubSubSubSection{Proof of `1DevFull' team's 3rd place}

The 3rd place of `1DevFull' team is confirmed in the announcement by the organizer \ExhibitRef{RsvNews}.

Additionally, it was announced in the Telegram channel of the competition \ExhibitRef{LodTelegramPodium}.


\SubSubSubSection{Proof of \mrl being the recipient of the award}

The podium place of \mrl is confirmed by the electronic diploma
issued by the competition organizer \ExhibitRef{LodDiploma}.

That diploma does not mention the specific place \mrl and his team took.
His name is not mentioned in textual public records because the website of the hackathon
was recently renovated with the old news announcements containing individual names lost.

Instead, the recording of the stream with the team presenting the case
can serve as a proof \ExhibitRef{LodDefenseTeam}.
It is on the organizer's YouTube channel, which proves its authenticity.
\mrl is shown as a member of the team at the position of `Architecture + ML',
which is a key position.

Additionally, when the old announcements were deleted,
\MrLod
has personally confirmed \mrls award as a recommendation
on his LinkedIn page \ExhibitRef{LodRecommendation}.

The fact that \MrLod was <\dots> is confirmed by
the news announcement:

\ParagraphQuoteBy{%
    <\dots>%
}{News at the website of <\dots>}


\SubSubSubSection{Proof that the award is for excellence in the field of \fie}

In his LinkedIn recommendation, \MrLod mentions:

\ParagraphByExhibit{%
    ``The assessment criteria were:

    \begin{itemize}
        \item \ul{the software prototype};
        \item solving the main problem of the case holder;
        \item \ul{development and implementation};
        \item innovations;
        \item \ul{user interface and user experience};
        \item solving secondary problems;
        \item analytics."
    \end{itemize}
}{\MrLod}{LodRecommendation}

Of those criteria, at least three (1st, 3rd, and 5th) are purely aspects of software development,
while others are allied properties.
This proves that the award was in \mrls field of \fie.

The focus of the competition is also shown in the announcement:

\ParagraphQuoteByExhibit{%
    Over the course of 48 hours, 165 teams worked on solving Health \& Science cases,
    aimed at \ul{developing IT solutions} for medicine and healthcare.
    A total of 124 solutions were proposed by participants,
    and 40 teams advanced to the final of the competition.
    \ul{Data analysis, digital transformation, Big Data, machine learning,
    Data Science, artificial intelligence, Web, Mobile} –
    these and other tasks were the focus of the hackathon cases.%
}{News at the website of \QRsv}{RsvNews}


\SubSubSubSection{Proof that the award is national}

The announcement on the website of Ministry of Science reads:

\ParagraphQuoteByExhibit{%
    Teams of IT specialists, designers, and managers in the digital economy
    aged 18 and older can participate in the competition.%
}{Ministry of Science and Higher Education of Russia}{MinistryOfScience}

Also, there was no geographical limitation within Russia according to this announcement:

\ParagraphQuoteByExhibit{%
    `\dots look at the results:
    \ul{4455 participants, 12 regional venues}, 6 case assignments, 124 solutions.
    I am very pleased that there are so many of you.
    This semifinal turned out to be truly massive, and I hope it was productive and interesting for you.

    `It is gratifying that not only IT specialists
    but also medical professionals participated in the hackathon,
    and some of them have experience in creating IT startups.
    \ul{The format of the competition brings together people from different parts of Russia},
    allowing them to form strong digital teams
    and creating strong interregional connections within the IT community.
    We saw \ul{many teams whose members live in different regions of our vast country},'
    said Alexey Agafonov, Deputy General Director of the ANO `Russia – Land of Opportunity.'%
}{News at the website of \QRsv}{RsvNews}


\SubSubSubSection{Proof of the national recognition of the award}

`Digital Breakthrough' hackathons were announced in the website
of the Ministry of Science and Higher Education of Russia:

\ParagraphQuoteByExhibit{%
    The All-Russian competition `Digital Breakthrough'
    is one of the \ul{flagship projects of the presidential platform `Russia – Land of Opportunity'}
    and is part of the events planned for the Year of Science and Technology.%
}{Ministry of Science and Higher Education of Russia}{MinistryOfScience}

This is what the website of the organizer reads:

\ParagraphQuoteByExhibit{%
    The third hackathon of the third season of the All-Russian competition `Digital Breakthrough,'
    the \ul{flagship project of the presidential platform} `Russia – Land of Opportunity,'
    dedicated to the theme of `Medicine, Healthcare, Science,' has concluded.%
}{News at the website of \QRsv}{RsvNews}

% English name is from here: http://en.kremlin.ru/events/president/news/71180
The organizer of the competition is a \QRsv,
a non-profit established by a decree of the president of Russia:

\ParagraphByExhibit{%
    ``In order to create conditions for increasing social mobility
    and ensuring personal and professional self-realization of citizens, I decree:

    \begin{enumerate}

        \item To consider it expedient to establish an autonomous non-profit organization
        `Russia – Land of opportunities' (hereinafter referred to as the non-profit organization).

        \item To establish that:

        \begin{enumerate}[label=\alph*)]
            \item The founder of the non-profit organization on behalf of the Russian Federation
            is the Administration of the President of the Russian Federation;\dots"
        \end{enumerate}
    \end{enumerate}
}{\MrPutinT}{RsvDecree}

Together that means that the award is recognized nationally.
