\subsubsection{\GSchool}
\label{subsubsec:RoleGran}

\SubSubSubSection{Context}

\GSchool is a manufacturer of educational kits for children,
and a franchise and a chain of development centers for children with some programs for adults.

\mrl served as the CTO of the company in 2015--2016, which will be shown below.


\SubSubSubSection{Proof of \mrls performing a critical role in the business of Mr. Sergey Gran}

Mr. Sergey Gran, the founder and the owner of \GSchool, writes the following in his letter:

\ParagraphQuoteByExhibit{%
    I had been working with Alexey Inkin since 2011 when he became my assistant in IT tasks.
    He soon became the Chief Technical Oficer of the company and remained one
    until he resignedin 2016. His duties included:

    \begin{enumerate}

        \item Creating websites including backend programming.

        \item Integrating external information systems: payments, advertising tracking, email subscriptions,
        newsletters, affiliate marketing management.

        \item Programming systems to track learning.

        \item Hiring other programmers and other freelancers.

    \end{enumerate}

    Alexey's most important contribution to my company was that \ul{he was in charge of all IT-related work} we had.

    As a result of Alexey's work, we implemented eficient IT solutions
    in the areas of customer learning management, sales, payment procesing, email marketing,
    affiliate marketing, and others.
    This allowed the company to \ul{accelerate its growth severalfold
    and helped increase the company's revenues fourfold} during the period from 2014 to 2015.

    At the peak, my company had \ul{over a hundred teachers, over 2500 students,
    and over a hundred active affiliate marketing partners} simultaneously.

    This scale became posible, among other things, thanks to efective IT solutions
    implemented by Alexey in various areas of the company's operations.%
}{\MrGranT}{LetterGran}


\SubSubSubSection{Proof that \GSchool is a distinguished organization}

The YouTube channel of Mr. Sergey Gran that promotes his school
has over 1.2 million views of the videos in total \ExhibitRef{GranYouTube}.

The profile of his school on VK.com, a popular social network in Russia,
has over 16 thousand followers and explains the products \ExhibitRef{GranSchoolVk}.

KTRK, the national television in Kyrgyzstan, has aired a story
about a development center for kids in Bishkek, the capital of Kyrgyzstan,
with the focus on the methodology by Mr. Sergey Gran and the educational kits
that his school manufactures.
See the screenshots and the transcript in \ExhibitRef{ZamanaVideo}.
The prominence of this TV channel is proved by the BBC's guide to Kyrgyzstan media
\ExhibitRef{BbcUtrk}.

The central television in Chelyabinsk Region of Russia
has run a discussion on engineer education for kids and teens,
and one of Mr. Gran's franchisees was among the speakers
on the same panel with prominent education figures like
Vitaliy Litke, Deputy Minister of Education and Science of the Chelyabinsk Region
\ExhibitRef{ChelyabinskTv}.

In the video, the educational kits produced by \GSchool are showcased,
with the school's brand clearly visible on two of those kits.

The significant number of followers and media coverage in two countries
make the \GSchool a distinguished organization for the purpose of this petition.
